\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\ or \\ Charting antigenic drift and evolutionary success of seasonal influenza lineages

### 2013-01-29 flux.tex
Annotate drift figure with cluster labels.

%%% map %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/map}
	\caption{\textbf{Antigenic locations of A/H3N2, A/H1N1, B/Vic and B/Yam viruses showing evolutionary relationships between virus samples.} 
	Circles represent a posterior sample of virus locations and have been shaded based on year of isolation.
	Antigenic units represent two-fold dilutions of the HI assay.
	Absolute positioning of lineages, e.g.\ A/H3N2 and A/H1N1, is arbitrary.
	Lines represent mean posterior diffusion paths when virus locations are fixed.
	Antigenic clusters are labeled after vaccine strains present within clusters.
	Abbreviated strains are as follows Hong Kong/68, England/72, Victoria/75, Bangkok/79, Sichuan/87, Beijing/89, Beijing/92, Wuhan/95, Sydney/97, Fujian/02, Wisconsin/05, Perth/09 (A/H3N2), USSR/77, Singapore/86, Beijing/95, New Caledonia/99, Solomon Islands/06 (H1N1), Victoria/87, Hong Kong/01, Brisbane/08 (Vic), Yamagata/88, Shanghai/02, Wisconsin/10 (Yam).} 
	\label{map} 
\end{figure}

@@

%%% drift %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=0.75\textwidth]{figures/drift}
	\caption{\textbf{Antigenic drift of A/H3N2, A/H1N1, B/Vic and B/Yam viruses showing evolutionary relationships between virus samples.} 
	Antigenic drift is shown in terms of change of location in the first antigenic dimension through time.
	Circles represent a posterior sample of virus locations and have been shaded based on year of isolation.
	Antigenic units represent two-fold dilutions of the HI assay.
	Relative positioning of lineages, e.g.\ A/H3N2 and A/H1N1, in the vertical axis is arbitrary.
	Lines represent mean posterior diffusion paths when virus locations are fixed.} 
	\label{drift} 
\end{figure}

>>>>

%%% map %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/map}
	\caption{\textbf{Antigenic locations of A/H3N2, A/H1N1, B/Vic and B/Yam viruses showing evolutionary relationships between virus samples.} 
	Circles represent a posterior sample of virus locations and have been shaded based on year of isolation.
	Antigenic units represent two-fold dilutions of the HI assay.
	Absolute positioning of lineages, e.g.\ A/H3N2 and A/H1N1, is arbitrary.
	Lines represent mean posterior diffusion paths when virus locations are fixed.
	Antigenic clusters are labeled after vaccine strains present within clusters, and are abbreviated from Hong Kong/68, England/72, Victoria/75, Bangkok/79, Sichuan/87, Beijing/89, Beijing/92, Wuhan/95, Sydney/97, Fujian/02, Wisconsin/05, Perth/09 (A/H3N2), USSR/77, Singapore/86, Beijing/95, New Caledonia/99, Solomon Islands/06 (H1N1), Victoria/87, Hong Kong/01, Brisbane/08 (Vic), Yamagata/88, Shanghai/02, Wisconsin/10 (Yam).} 
	\label{map} 
\end{figure}

@@

%%% drift %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=0.75\textwidth]{figures/drift}
	\caption{\textbf{Antigenic drift of A/H3N2, A/H1N1, B/Vic and B/Yam viruses showing evolutionary relationships between virus samples.} 
	Antigenic drift is shown in terms of change of location in the first antigenic dimension through time.
	Circles represent a posterior sample of virus locations and have been shaded based on year of isolation.
	Antigenic units represent two-fold dilutions of the HI assay.
	Relative positioning of lineages, e.g.\ A/H3N2 and A/H1N1, in the vertical axis is arbitrary.
	Lines represent mean posterior diffusion paths when virus locations are fixed.
	Antigenic clusters are labeled after vaccine strains present within clusters, and are abbreviated from Hong Kong/68, England/72, Victoria/75, Bangkok/79, Sichuan/87, Beijing/89, Beijing/92, Wuhan/95, Sydney/97, Fujian/02, Wisconsin/05, Perth/09 (A/H3N2), USSR/77, Singapore/86, Beijing/95, New Caledonia/99, Solomon Islands/06 (H1N1), Victoria/87, Hong Kong/01, Brisbane/08 (Vic), Yamagata/88, Shanghai/02, Wisconsin/10 (Yam).} 
	\label{drift} 
\end{figure}
